Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Don't use any sorting, this means the bibliography gets ordered by appearance!
Some wording improvements, eliminated an unneeded paragraph, details about the processing of files. Added details of building matcher.

% Use the excellent biblatex package with apa style
% minnames=1,maxnames=2 - abbreviates all author names in citations
% hyperref - links in pdf
\RequirePackage[
  url = false,
  hyperref = true,
  style = ieee,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

@@

Like a mix, messages sent over an onion routing network were encrypted with
their routing information and delivered to an intermediate server for forward
delivery.  Unlike the mix however, messages delivered using the onion routing
network were encrypted multiple times, each 'layer' using a different key and
routing instructions. The first node in a chain would only be able to encrypt
the routing instructions to deliver the message to the next node. Each node in
the sequence decrypting a layer until the complete message is decrypted and
transmitted to the destination.

@@

When the first node in the circuit receives a cell, it removes a layer by
decrypting the message using it's session key. The cell is delivered along the
circuit and at each node a layer is removed until the cell is completely
decrypted and can be delivered successfully. Since circuits can take some time
to build, they are pre-emptively created at regular intervals

@@

The experiment was run over the course of 8 weeks yielding three sets of sample
data.

@@

@@

When a histogram of packet sizes for each of the packet traces is produced, a
pattern becomes very apparent.

@@

Investigating more closely, by examining individual packet traces some
significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
phase of data captured. The first few packets contain 0 bytes of data, these
are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
a TCP/IP connection. Following that only two packet sizes are seen for HTTP
connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
152. This knowledge can be used to build a very rudimentary classification
algorithm to identify Tor traffic, as seen in the pseudo-code below:

@@

>>>>

% Use the excellent biblatex package with apa style
% minnames=1,maxnames=2 - abbreviates all author names in citations
% hyperref - links in pdf
\RequirePackage[
  sorting = none,
  url = false,
  hyperref = true,
  style = ieee,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

@@

Like a mix, messages sent over an onion routing network were encrypted with
their routing information and delivered to an intermediate server for forward
delivery.  Unlike the mix however, messages delivered using the onion routing
network were encrypted multiple times, each 'layer' using a different
encryption key and routing instructions. The first node in a chain would only
be able to encrypt the routing instructions to deliver the message to the next
node. Each node in the sequence decrypting a layer until the complete message
is decrypted and transmitted to the destination.

@@

@@

The experiment was run over the course of 8 weeks yielding three sets of sample
data:

@@

The data captured was in the form of 1MB capture files which were recombined
with mergecap and processed by NetAI \parencite{swinbut:2006fk} to produce ARFF
format files for use by Weka \parencite{Hall:2009p7662,Bouckaert:2010we}. NetAI
identifies flows inside the capture files and produces a number of statistics
to be used as attributes for classification.

@@

With some relative success classifying Tor traffic using unsupervised machine
learning techniques, the captures were examined for a heuristics based
classification approach. When a histogram of packet sizes for each of the
packet traces is produced, a clear distinction can between seen between the
sample sets:

@@

Investigating more closely, by examining individual packet traces some
significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
phase of data captured. The first few packets contain 0 bytes of data, these
are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
a TCP/IP connection. Following that only two packet sizes are seen for HTTPS
connections. For Tor sessions a range of packet sizes from 131 to 152. This
knowledge can be used to build a very rudimentary classification algorithm to
identify Tor traffic, as seen in the pseudo-code below:

@@

When examining the cases where the algorithm failed to identify Tor streams, in
all cases the session had failed to successfully initiate the handshake
required for a TCP session. Which meant that no meaningful data could have been
transmitted.
